---
title: "Brand loyalty and price-quality perceptions of hybrid maize seed in La Frailesca Chiapas, Mexico"
author: "Ciro Domínguez Méndez and Romain Frelat"
date: 'Last update: 23rd January 2023'
output:
  html_document: 
      keep_md: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is the accompanying script and data for the article **Brand loyalty and price-quality perceptions of hybrid maize seed in La Frailesca Chiapas, Mexico** by Ciro Domínguez Méndez, Jason Donovan, Romain Frelat, and C.S. Srinivasan currently in review. 
See the *Materials and Methods* section of the article for more details about the data and the method.

# 1. Preliminaries


### Load the packages
The analysis require the packages `lavaan` (v ≥ 0.6), `psych` (v ≥ 2.2.9), and `semPlot` (v ≥ 1.1.6).

```{r, message=FALSE}
library(lavaan)
library(psych)
library(semPlot)
```

If you get an error message, check that the R packages `lavaan`, `psych` and `semPlot` are installed correctly. If not, use the command: `install.packages(c("lavaan", "psych", "semPlot"))`.

### Load the dataset

The dataset containing the 12 variables for the 393 farmers is stored in the csv file `MaizeBrandPrice.csv`, and available for download [here](https://github.com/rfrelat/SEM_MaizeBrandPrice/raw/main/MaizeBrandPrice.csv)

The variables have been scaled so that all the values are within the same range, between -3 and 3. The questions (Q51 to Q58) followed a *7-point Likert scale*, including:  

- “Agree very much”: 3 
- “Agree”: 2
- “Kind of agree”: 1 
- “Do not agree or disagree”: 0 
- “Kind of disagree”: -1 
- “Disagree”: -2
- “Disagree very much”: -3

```{r loading}
tab <- read.csv("MaizeBrandPrice.csv")
dim(tab)
names(tab)
```



# 2. Confirmatory Factor Analysis


```{r CFA}
CFA.model <- 'quality  =~ Q51 + Q52
              value =~ Q53 + Q54
              willbuy =~ Q55 + Q56
              sacrifice =~ Q57 + Q58
              loyalty  =~ commitment + preference'

fitCFA <- cfa(CFA.model, data=tab, estimator="WLSMV")
summary(fitCFA, fit.measures=TRUE, standardized=TRUE)
```

```{r plotCFA}
semPaths(fitCFA, nCharNodes = 0, what='std', 
         style = "lisrel", rotation = 4)
```

```{r tableCFA}
standardizedSolution(fitCFA)[1:10,]
```


# 3 Structural Equation Modelling


```{r SEM}
model <- '  
  # measurement model
    quality  =~ Q51 + Q52
    sacrifice =~ Q57 + Q58
    value =~ Q53 + Q54
    willbuy   =~ Q55 + Q56
    loyalty  =~ commitment + preference
  # regressions
    quality ~ refprice
    sacrifice ~ sellprice
    value ~ sacrifice + quality + loyalty
    willbuy ~ value
'

fitSEM <- sem(model, data=tab, estimator="WLSMV")
summary(fitSEM, fit.measures=TRUE, standardized=TRUE)
```

```{r plotSEM}
semPaths(fitSEM, nCharNodes = 0, what='std', 
         style = "lisrel", rotation = 4)
```

```{r fitSEM}
fitmeasures(fitSEM, c("chisq.scaled", "df", "rmsea", "srmr", "gfi", "agfi", "cfi", "tli"))
```


